An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-12 EconGrowth2.Rnw
Added NSF acknowledgement.
Changed wording of the resampling section.

Under that assumption, it would not be surprising if the residual from 
any particular year had been observed in a different year. 
By applying randomly selected residuals [$\mathrm{abs}(\mathrm{rand}(r_t))$]
with randomly selected signs [$\mathrm{rand}(-1, 1)$]
to model predictions, we create a 
preliminary resampled GDP time series ($y_{prelim,resample,t}$):

\begin{equation} \label{eq:resample_y_prelim}
  y_{prelim,resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \mathrm{abs}(\mathrm{rand}(r_t)).
\end{equation}

\noindent{}The preliminary resample time series
can have non-unity first-year GDP ($y_{prelim,resample,0} \ne 1$).
If we had actually obtained the resampled GDP data series,
we would have indexed to a different first-year GDP value, 
such that \emph{every} resampled GDP time series starts with $y_{resample,0} = 1$.
We use

@@

Funding for Caleb Reese and Lucas Timmer was provided 
by the Jack and Lois Kuipers Applied Mathematics Endowment and 
the Calvin College Alumni Association. 
Partial support for Matthew Kuperus Heun was 
provided by a Calvin College Research Followship. 
Partial funding for Martin de Wit was provided 
by the South African National Research Foundation (NRF).\footnote{Any opinion, 
findings, and conclusions or recommendations expressed herein are those 
of the authors, and, therefore, NRF does not accept any liability in regard thereto.} 
The authors are grateful to Benjamin S. Warr (INSEAD) for providing 
the REXS database \citep{Warr:2012a}. 
The authors thank Loren L. Heun (Western Michigan University) 
for insightful critique of the statistical analyses presented herein.

>>>>

Under that assumption, it would be unsurprising if the residual from 
any particular year had been observed in a different year. 
To obtain a 
preliminary resampled GDP time series ($y_{prelim,resample,t}$),
we add
the absolute value of residuals 
from randomly-selected times $\left( \left| r_{\mathrm{rand}(t)} \right| \right)$
with randomly-selected signs [$\mathrm{rand}(-1, 1)$]
to model predictions.

\begin{equation} \label{eq:resample_y_prelim}
  y_{prelim,resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \left| r_{\mathrm{rand}(t)} \right|.
\end{equation}

\noindent{}We note that the preliminary resample time series
can have non-unity first-year GDP ($y_{prelim,resample,0} \ne 1$).
If we had actually obtained the resampled GDP data series,
we would have indexed to a different first-year GDP value, 
such that \emph{every} resampled GDP time series has $y_{resample,0} = 1$.
We use

@@

Funding for Caleb Reese and Lucas Timmer was provided 
by the Jack and Lois Kuipers Applied Mathematics Endowment and 
the Calvin College Alumni Association. 
Partial support for Matthew Kuperus Heun was 
provided by a Calvin College Research Followship. 
Partial funding for Martin de Wit was provided 
by the South African National Research Foundation (NRF).\footnote{Any opinion, 
findings, and conclusions or recommendations expressed herein are those 
of the authors, and, therefore, NRF does not accept any liability in regard thereto.} 
The authors are grateful to Benjamin S. Warr (INSEAD) for providing 
the REXS database \citep{Warr:2012a}. 
The authors thank Loren L. Heun (Western Michigan University) 
for insightful critique of the statistical analyses presented herein.
The computations in this paper were accomplished using dahl.calvin.edu, 
a Beowulf cluster built with support from the National Science Foundation's 
Major Research Instrumentation and Cyber Infrastructure programs, 
grant no. OCI-0722819.
